\speculake: Hiding Malware in Speculative Execution

### 2018-08-04 paper/figures.tex
made line plots greyscale friendly
figure updates

@@

\newcommand{\FigCacheMiss}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/cache_miss_dist}
    \caption{The Cache Hit/Miss Latency Distribution of an Intel
        Xeon-1270. Measured by timing accesses to cached/uncached memory. 
        Typical cache miss resolution takes 6x longer than a cache hit.}
    \label{fig:cache-miss}
\end{figure}
}

>>>>

\newcommand{\FigSpectreOne}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/spectre_1_training.png}
    \caption{When using speculative buffer overflow the direct branch predictor
    must be trained on input data before it can mis-speculate a branch. 
    Over an independent number of training 
    rounds we measure the resulting hit rate fraction of trials where the 
    speculative gadget is able to perform the intended cache load. We find 
    that around 200 benign training branches are required before a branch 
    can be mis-speculated with discernable hit rate fraction. Note that a 
    1\% signal is generally significant enough to discern as background cache noise 
    is minimal in an ideal scenario.}
    \label{fig:spectre-one}
\end{figure}   
}

\newcommand{\FigSpecMeasureNP}{
\begin{figure*}[t]
     \centering
        \includegraphics[width=0.9\textwidth]{figures/Speculative_measurements_no-parity.png}
    \caption{The speculative primitive allows for a limited number of instructions
    to be completed speculatively, dependent on multiple factors. The ROB 
    capacity aligns directly with the upper bound of nop instructions 
    that can be completed speculatively, while other constraints bound more 
    complex instructions.}
    \label{fig:spec-capacity-np}
\end{figure*}
}

\newcommand{\FigSpecMeasureParity}{
\begin{figure}[b]
     \centering
        \includegraphics[width=1.05\linewidth]{figures/Speculative_measurements_parity.png}
    \caption{Trigger and payload processes must share CPU resources as they 
        must be performed on the same hyperthread or associated parity hyperthreads. 
        Processes on the parity hyperthreads (cool colors) denoted by (P) accomplish a 
        significantly lower number of instructions as compared with processes 
        on the same hyperthread (warm colors).}
    \label{fig:spec-capacity-parity}
\end{figure}
}

@@

\newcommand{\FigCacheMiss}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/cache_miss_dist}
    \caption{The Cache Hit/Miss Latency Distribution of an Intel
        Xeon-1270 and AMD Epyc 7251. Measured by timing accesses to cached/uncached memory. 
        Typical cache miss resolution takes 6x longer than a cache hit.}
    \label{fig:cache-miss}
\end{figure}
}
